---
title: "myMap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myMap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myMap)

```

<p> myMap is a package implementing an R6 class constructor to download a map from Stamen API:[http://maps.stamen.com].</p>
<p> The constructor consists of 3 public methods and a private method. initialize method starts the function as it is called with the appropriate arguments.
## Call
<p> A new object will be generated as the constructor ic called:</p>
```{r}
myMap = MapStamen$new(left = -124.409591, bottom = 32.534156,
                      right = -114.131211, top = 	42.009518,
                      mapType = "terrain-background", Zoom = 8)
```

<p> This call generates a new object named "myMap" which is actually a map extracted from Stamen API.</p>
## Arguments
<p> A map which is aimed be extracted from Stamen should be defined by a box. The coordinates of the lower-left and upper-right points of the box should therefor be passed as the arguments.</p>
* left: Provides the lower-left longtitude of the box.
* bottom: Provides the lower-left latitude of the box.
* right: Provides the upper-right longitude.
* top: Provides the upper-right latitude.

* <p>mapType: Provides the type of interest for map to be extracted out. It can be one of the following: "terrain", "terrain-background", "terrain-labels", "terrain-lines", "toner", "toner-2010", "toner-2011", "toner-background", "toner-hybrid",  "toner-labels", "toner-lines", "toner-lite", "watercolor" .</p>
<p> Each of these types will show a special characteristic of the area of interest. For the details see:[http://maps.stamen.com] </p>

* Zoom: Provides the zoom level.

## Methods

### showMap()
This method will show the myMap:
```{r}
myMap$showMap()
```
<p>This is the map of the area of interest for the mapType = "terrain-background".</p>

<p> If we set mapType = "terrain":</p>

```{r}
myMap = MapStamen$new(left = -124.409591, bottom = 32.534156,
                      right = -114.131211, top = 	42.009518,
                      mapType = "terrain", Zoom = 8)

myMap$showMap()
```


### saveMap()
This method will save a png file of myMap in the working directory:
```{r}
myMap$saveMap()
```

### ClGoodday()
This method display the No. of healthy days in California in 2019:
```{r}
myMap$ClGoodday()
```

### ClModday()
This method display the No. of moderate days in California in 2019:
```{r}
myMap$ClModday()
```

### ClUnhealthyDay()
This method display the No. of unhealthy days in California in 2019:
```{r}
myMap$ClUnhealthyDay()
```

